Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-14 paper/ms.tex
update manuscript
Update manuscript with secondary line search
Co-authored-by: georgezhou <george.zhou@cfa.harvard.edu>

\edit1{George TODO: please describe the formal secondary line search
in more depth in this paragraph} We searched for secondary lines in
the CHIRON spectra by cross-correlating against a {\bf template of
some kind}.  This rules out lines with flux ratios of $\approx 2\%$,
if the lines are well-separated in velocity.  To derive the star's
physical parameters, we cross-correlated the template against {\bf
something}, and used the {\bf \texttt{nameofcode}}.  We measured the
radial velocities through a least-squares deconvolution of the
observed spectra against the same synthetic template.  The resulting
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

\subsubsection{Not SB2}
As described in Section~\ref{subsec:chiron}, we searched the CCFs of
the CHIRON spectra to determine whether \tn\ is double-lined.  For a
stellar companion well-separated in velocity, this typically reveals
companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
purposes, in Figure~\ref{fig:fpscenario} we have assumed a
flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).

@@

While we hope that RV observations will be pursued, data acquired
during the first TESS mission extension may also help in
understanding the system
\citep{bouma_extend_2017,huang_expected_2018}.  Any misalignment
between the star's spin axis and the planet's orbit should induce
nodal precession, which could yield large changes in the transit
duration given the system's high impact parameter.
If observed, this could be a spectroscopy-free method for 
confirming the planet

>>>>

We derived radial velocities and spectroscopic line profiles from the
CHIRON observations using a least-squares deconvolution of the spectra
against non-rotating synthetic spectral templates
\citep{donati_1997_spectropolarimetric}. The spectral templates were
generated using ATLAS9 atmosphere models \citep{Castelli:2004} with
the \texttt{SPECTRUM} script \citep{gray_1994_spectrum}. These line
profiles were fitted with a broadening kernel that describes the
rotational, radial-tangential macroturbulent, and instrumental
broadening of the spectrum. The rotational and macroturbulent
broadening are computed per \citet{gray_2005_book}, following the
methods described in \citet{zhou_2018_hd106315obliq}. We fitted the
line profile from each observation independently, yielding the radial
velocities listed in Table~\ref{tab:rvs} and shown in
Figure~\ref{fig:followup}. We found a mean rotational broadening
velocity of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
macroturbulent broadening of $v_\mathrm{Mac} = 8.4 \pm 2.9
\mathrm{km\,s}^{-1}$.

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously
obtained using the Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.
% TODO note to Zhou: inflated Fe/H uncertainty by factor of 2.

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines were found. To determine our detection limits to a blended
spectroscopic companion, we injected a second set of lines to the mean
least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux
ratio $F_2/F_1$. The recovery results showed that for rotational
broadenings of the secondary of $5$, $15$,
and $25\,\mathrm{km\,s}^{-1}$, we were able to exclude sources with
flux fractions $F_2/F_1$ brighter than roughly $0.03$, $0.08$, and
$0.20$, provided that the secondary was separated from the primary by
at least $\approx 15\,{\rm km\,s}^{-1}$.  At smaller velocity
separations, the injected lines begin to blend with the target
spectrum.

@@

\subsubsection{Not SB2}
We determined our detection limits to blended spectroscopic companions
using the CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, this
would have revealed companions with flux fractions $F_2/F_1 \gtrsim
3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
For bound companions this is justified through reasoning that coeval
binary companions to \tn\ would have both longer rotation periods and
smaller stellar radii, and therefore smaller equatorial velocities.

@@

While we hope that RV observations will be pursued, data acquired
during the first TESS mission extension may also help in
understanding the system
\citep{bouma_extend_2017,huang_expected_2018}.  Any misalignment
between the star's spin axis and the planet's orbit should induce
nodal precession, which could yield large changes in the transit
duration given the system's high impact parameter.
If observed, this could be a spectroscopy-free method for 
confirming the planet.
